Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine comoving star pairs from low-resolution spectroscopic follow-up

### 2017-06-03 paper/comoving-followup.tex
captions

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{wavelength_gp.pdf}
  \end{center}
  \caption{%
    \todo{Stuff}
    \label{fig:wavelength-GP}}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{sample_spectra.pdf}
  \end{center}
  \caption{%
    \todo{Stuff}
    \label{fig:sample-spectra}}
\end{figure}

>>>>

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{wavelength_gp.pdf}
  \end{center}
  \caption{%
    A visualization of the pixel-to-wavelength model determined from a single
    wavelength comparison lamp spectrum.
    Black markers show the fit pixel centroids for known Hg or Ne emission
    lines and the residual wavelength value between the linear + GP model and
    the true emission line centroid.
    The non-shaded region shows the section of spectrum where the comparison
    lamp spectrum has sufficient line density to determine the wavelength
    solution; shaded regions are masked from the resulting spectra.
    Organge envelope shows the root-variance of the Gaussian process component
    of the model, which can be interpreted as inherent uncertainties on the
    wavelength calibration as a result of the model flexibility.
    \label{fig:wavelength-GP}}
\end{figure}

\begin{figure}[htbp]
  \begin{center}
    \includegraphics[width=0.9\linewidth]{sample_spectra.pdf}
  \end{center}
  \caption{%
    A section of 10 randomly selected target spectra from this work.
    Spectral fluxes are normalized to 1 at $\lambda = 5500~{\rm \AA}$ and the
    offsets are chosen to separate the spectra for visualization.
    The spectra are smoothed with a Gaussian filter with root-variance $\sigma
    = 2~{\rm \AA}$.
    \label{fig:sample-spectra}}
\end{figure}
